A preliminary constraint grammar for Russian

### 2015-03-30 2015-nodalida-ruscg/ruscg.tex
concl.
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59574 72bbbca6-d526-0410-a7d9-f06f51895060
fill out sections
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59575 72bbbca6-d526-0410-a7d9-f06f51895060

  \item[ Incomplete barrier:] xxx 

@@

@@

>>>>

  \item[ Incomplete barrier:]  Some rules suffered from incomplete barriers, which is something that would
     benefit from a more systematic treatment.

@@

We have a number of plans for future work, the first is increasing the precision of the grammar without
decreasing recall. Secondly we would like to add syntactic function labelling and dependency analysis. For 
the dependency analysis we would like to reuse the Giellatekno dependency grammar as in \cite{antonsen10}.

The development workflow could also be improved, for example during the testing of each rule we could
save the correct decisions of the grammar and gradually build up a tagged development corpus for the language.

Also it is worth noting that although Russian has a great deal of non-free resources, this paper also presents
a method which is promising for smaller or lesser-resourced Slavic languages such as Sorbian, Rusyn or Belarusian. Instead
of hand-annotating a large quantity of text, it may be more efficient to work on grammatical resources --- such
as a morphological analyser and constraint grammar --- and use 
them alongside a smaller quantity of high-quality annotated text.

@@

This paper has presented a preliminary constraint grammar for Russian. The constraint grammar 
is high recall and improves the performance over a simple HMM-based tagger. It also shows 
state-of-the-art performance for the stress-placement task.
